%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Kai Breese} \\ \vspace{1pt}
    \small 925-786-5550 $|$ \href{mailto:kai.breeze@me.com}{\underline{kai.breeze@me.com}} $|$ 
    \href{https://www.linkedin.com/in/kaibreese}{\underline{linkedin.com/in/kaibreese}} $|$
    \href{https://github.com/ninjakaib}{\underline{github.com/ninjakaib}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California San Diego}{La Jolla, CA}
      {Bachelor of Science in Data Science}{Sep. 2021 -- March 2025}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
  {Machine Learning Engineer Intern}{June 2024 -- Present}
  {XiFin, Inc.}{San Diego, CA}
  
  \resumeItemListStart
  \resumeItem{Developed \textbf{IDE coding assistant} using open-source LLMs on AWS SageMaker, enabling context-aware code suggestions, inline editing, and real-time autocomplete.}
  \resumeItem{Built \textbf{automated insurance appeal letter system} with knowledge graphs and multimodal LLMs, cutting manual processing time.}
  \resumeItem{Optimized \textbf{insurance pricing pipeline} to achieve 90x throughput with multiprocessing and custom C backends.}
  \resumeItem{Redesigned pricing database to reduce data duplication by \textbf{75\%} through normalization and optimized parsing.}
  \resumeItem{Created a \textbf{no-code deployment tool} for easy model deployment on AWS using custom Docker containers.}
  \resumeItem{Enhanced chatbot with streaming vision, reducing incorrect answer rate from \textbf{50\% to 15\%}.}
  \resumeItem{Developed a new \textbf{RAG pipeline} for agentic retrieval and visual document understanding.}
  \resumeItem{Designed an \textbf{AI SQL generator} with context-guided outputs for complex, accurate query formulation.}
  \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software Developer}{Mar. 2024 -- July 2024}
      {Clayton Health, LLC}{San Diego, CA}
      \resumeItemListStart
        \resumeItem{Built custom e-commerce platform for Shopify using Liquid driving \textbf{\$100K in sales} within first 6 months}
        % \resumeItem{Engineered automated order processing system through supplier and shipper integrations, streamlining operations and reducing manual processing time}
        \resumeItem{Implemented automated email marketing campaigns leading to \textbf{8\% conversion rate}}
        \resumeItem{Worked directly with CEO to rapidly bring new features from concept to production}
      \resumeItemListEnd
    
    \resumeSubheading
      {Sales Consultant}{Oct. 2023 -- Apr. 2024}
      {Verizon}{San Diego, CA}
      \resumeItemListStart
        \resumeItem{Ranked top 5 in San Diego district generating an average of over \$100/hr in company profits}
        \resumeItem{Created long term relationships with high-value business clients to drive repeat sales}
      \resumeItemListEnd
    
    \resumeSubheading
      {Computer Science Tutor}{Mar. 2023 -- Feb. 2024}
      {TheCoderSchool}{San Diego, CA}
      \resumeItemListStart
        \resumeItem{Led one-on-one and classroom based sessions, teaching students in ways they can easily understand and relate to}
        \resumeItem{Helped students create over 100 unique projects including games, websites, and assignments}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Machine Learning Hardware Accelerator Chip}}{Sept. 2024 -- Present}
          \resumeItemListStart
\resumeItem{Implemented the \textbf{first ASIC-based L-Mul algorithm} in simulation, achieving up to \textbf{88.9\% area}, \textbf{99.6\% power}, and \textbf{80.7\% delay} improvements versus IEEE-754 multipliers (FP8 to FP32) with <0.1\% accuracy loss.}
\resumeItem{Designed a full \textbf{accelerator core in Python} using PyRTL with a custom VLIW-style simulation framework and pipelined execution for efficient resource utilization.}
\resumeItem{Developed a rudimentary \textbf{compiler} that converts a model’s computational graph into an optimized instruction sequence via matrix tiling and topological sorting.}
\resumeItem{Integrated RTL design, automated CI testing, and openROAD physical hardening to validate performance and guide design decisions.}
\resumeItemListEnd

      \resumeProjectHeading
          {\textbf{AI Healthcare Assistant} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{June 2023 -- Oct. 2023}
          \resumeItemListStart
            \resumeItem{Developed a conversational AI phone call service before similar products from OpenAI came to market, achieving 80\% API cost reduction over comparable solutions}
            \resumeItem{Designed SQL relational database with nutritional information scraped from the web}
            \resumeItem{Fine-tuned LLMs and deployed with AWS for real-time streaming and high-user load capacity}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, TypeScript, C/C++, Excel} \\
     \textbf{Frameworks}{: FastAPI, Flask, Gradio, Svelte, Nginx, React, Liquid} \\
     \textbf{Developer Tools}{: Git, Docker, Anaconda, Yosys, Jupyter, Jira, VS Code, ChatGPT} \\ 
     \textbf{Libraries}{: pandas, NumPy, PyTorch, matplotlib, sklearn, transformers, langchain, Cython, PyRTL} }} \\
     \textbf{Cloud}{: AWS Sagemaker, Lambda, S3, RDS, ECR, EC2, API Gateway, Oracle DB}
 \end{itemize}


%-------------------------------------------
\end{document}
